upwell_IDX

### 2020-05-04 upwell_IDX.Rmd
update

```{r}
# Installing and loading libraries
## devtools::install_github("robwschlegel/coastR")
## devtools::install_github("retostauffer/Rfoehnix")
library(tidyverse)
library(circular)
#library(foehnix)
library(gridExtra)
library(geosphere)
library(heatwaveR)
library(coastR)
library(openair)
```

>>>>

```{r}
# Installing and loading libraries
## devtools::install_github("robwschlegel/coastR")
## devtools::install_github("retostauffer/Rfoehnix")
library(tidyverse)
library(circular)
#library(foehnix)
library(gridExtra)
library(geosphere)
library(heatwaveR)
library(coastR)
library(openair)

load("Data_coast_angle/site_list_v4.2.RData")
load("Data_coast_angle/SACTN_daily_v4.2.RData")
load("Data_coast_angle/data_prod_dates")

site_list_sub <- site_list %>%
  filter(coast == "wc") %>%
  filter(length > 3650)

site_list_sub <- site_list_sub[c(-2, -3, -5, -6, -7,-9, -12, -13, -14),] # Here I keep all the sites with temperature obtained up to
# 2017 -kommetjie and Yzerfontein was removed as temperatures started in 1990s. 
# I took up till 2017 because the G1SST data starts frm 2010-present. To create a long time series to run through the heatwaveR algorithm, this was needed.
# save(site_list_sub, file = "Data_coast_angle/site_list_sub.Rdata")

SACTN_US <- SACTN_daily_v4.2 %>%
  left_join(site_list[,c(4,13)], by = "index") %>%
  filter(index %in% site_list_sub$index) %>%
  separate(index, into = c("site", "src"), sep = "/", remove = FALSE) %>%
  dplyr::rename(insitu_temp = temp)
```

# Creating a table showing the start and end dates for each of the data products used in this project

```{r}

```
